### 2017-10-09 paper/incomeShocks-jde-r1.tex
Respond to R1's question on wave 1 assets
The discussion of assets interacted with crop loss was made a separate
section prior. This revision adds log of crop loss interacted with
log of assets and results where the first wave crop loss is dropped
because it might affect wave 1 assets.

The new section is edited to reflect changes in results.

All results are combined into one table, so three original analysis
files are deleted because their results show up elsewhere.

To further investigate whether the response to shock vary by household
characteristics, we also estimated individual level fixed effects versions 
of equation (\ref{eq:fixed_effects2}),
\begin{align}
Y_{i,t} &=  \beta_1 S_{i,t}  +  \beta_2 S_{i,t} \times X_{i,1} +
\alpha_{t} + \mu_i + \varepsilon_{i,t},   
\label{eq:fixed_effects2} 
\end{align}
where $X_{i,1}$ are either age group, assets holdings at the time of 
the first survey or education levels of the respondent or household head.
Table \ref{tab:agegroups} shows the effects of crop losses by age groups.
The effect of crop losses are concentrated for women younger than 32
years of age, although as discussed above there appears to be 
substantial measurement error in self-reported age.

@@

As crop loss may affect asset levels, we should ideally use assets owned 
prior to any observed shocks.
Unfortunately, we do not have data available on assets prior to the first 
survey round.
We therefore use assets owned in the first round, even though 
shocks that occurred before the first round likely affect these.
Appendix Table \ref{tab:assets} expands the main results above by adding 
the interaction of crop loss and assets.
In all cases, the coefficients for the interaction of assets in round 1 and 
crop loss are small and not statistically significant,
suggesting that wealth level may not be a determining
factor regarding the contraceptive use decision following shocks. 
There are three potential reasons why we do not find an effect of wealth.
First, the opposite predicted effects of wealth cancel each other out.
Second, even ``wealthy'' households in this area are  poor and
there may be too little variation in wealth level to capture any effects.
Third, there is likely measurement error in the asset levels. 
There are significant variations in reported household asset levels between 
periods, and it is possible that part of these variations are a result of 
reporting errors rather than actual variation in wealth.

@@

For women with 7 or more years of education---which is the largest
group in the sample---the estimates are consistent with the 
main results, with statistically significant effects of crop loss 
across all outcomes, except use of modern contraceptives.
The reductions in likelihoods of being pregnant or having a birth
following crop loss are now close to each other at 17 and 19 percentage
points, and the increase in use of any contraception is 10 percentage
points.
For the other two education groups, the effects are mostly insignificant.

Using the household head's education level leads to broadly 
similar results as for the respondents' education. 
A crop loss leads to reductions in pregnancy and birth by
15 and 19 percentage points and an increase of 8 percentage points
in the use of any contraception.
For the middle-education group there is a statistically significant
effect on birth, but the impacts on the other outcomes are close to zero and
not statistically significant.
The no-education group shows a large and statistically significant
effect of contraceptive use following a crop loss, but the
effects on pregnancy and birth are about half the size and
not statistically significant.

>>>>

To further investigate whether the response to shock vary by household
characteristics, we also estimated individual level fixed effects versions 
of equation (\ref{eq:fixed_effects2}),
\begin{align}
Y_{i,t} &=  \beta_1 S_{i,t}  +  \beta_2 S_{i,t} \times X_{i,1} +
\alpha_{t} + \mu_i + \varepsilon_{i,t},   
\label{eq:fixed_effects2} 
\end{align}
where $X_{i,1}$ are either age group, assets holdings at the time of 
the first survey or education levels of the respondent or household head.
Table \ref{tab:agegroups} shows the effects of crop losses by age groups.
The effect of crop losses appear to be mainly concentrated among women 
younger than 32 years of age, although as discussed above there appears 
to be substantial measurement error in self-reported age.

@@

Appendix Table \ref{tab:assets} expands the main results above by adding 
the interaction of crop loss and assets, both for the main specification
and using log of crop loss and log of assets.
As crop loss may affect asset levels, we should ideally use assets owned 
prior to any observed shocks.
Unfortunately, we do not have data available on assets prior to the first 
survey round.
We therefore present two different specifications.
The first specification includes all waves, even though shocks that 
occurred before the first round potentially affect the asset level.
The second specification excludes wave 1 shocks, which results in
substantial loss of sample size and variation in crop loss.

For pregnancy and births, the coefficients for the interaction of assets 
in round 1 and crop loss are small and not statistically significant,
suggesting that wealth level may have a limited impact on fertility
decisions following shocks. 
The interactions are more likely to have a statistically significant
effect for contraceptive use, although the coefficients are still
small (recall that assets are measured in 1,000,000 TZS).

There are three potential reasons why we do not find an effect of wealth.
First, the opposite predicted effects of wealth cancel each other out.
Second, even ``wealthy'' households in this area are  poor and
there may be too little variation in wealth level to capture any effects.
Third, there is likely measurement error in the asset levels. 
There are significant variations in reported household asset levels between 
periods, and it is possible that part of these variations are a result of 
reporting errors rather than actual variation in wealth.

@@

For women with 7 or more years of education---which is the largest
group in the sample---the estimates are consistent with the 
main results, with statistically significant effects of crop loss 
across all outcomes, except use of modern contraceptives.
The reductions in likelihoods of being pregnant or having a birth
following crop loss are now close to each other at 16 and 19 percentage
points, and the increase in use of any contraception is 8 percentage
points.
For the other two education groups, the effects are mostly insignificant.

Using the household head's education level leads to broadly 
similar results as for the respondents' education. 
A crop loss leads to reductions in pregnancy and birth by
14 and 19 percentage points and an increase of 7 percentage points
in the use of any contraception.
For the middle-education group there is a statistically significant
effect on birth, but the impacts on the other outcomes are close to zero and
not statistically significant.
The no-education group shows a large and statistically significant
effect of contraceptive use following a crop loss, but the
effects on pregnancy and birth---while close to the 7 or more 
years of education group---are not statistically significant.
